---
title: "Homework 5"
author: "Shane W."
date: "February 13, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Homework 5

Utilized Libraries and Establishing Working Directory
```{r, echo = TRUE}
library(tidyr)
library(dplyr)
getwd()
```

### Question 1: Data Munging

A. Importing, creating, and assigning dataframe df
```{r, echo=TRUE}
df <- read.csv(file = "yob2016.txt", header = FALSE, sep = ";")
colnames(df) <- c("Name","Gender","#Named2016")
```

B. Display the df
```{r, echo=TRUE}
summary(df)
str(df)
```

C. Discover the duplicate
```{r, echo=TRUE}
#Duplicate noted to have 3 'y's
grep("y{3}$",df$`Name`,value=TRUE)
```

D. Remove the Duplicate
```{r, echo=TRUE}
y2016 <- df[-grep("y{3}$",df$`Name`),]
str(y2016)
```

### Question 2: Data Merging

A. Importing Year of Births 2015
```{r, echo=TRUE}
y2015 <- read.csv(file= "yob2015.txt", header = FALSE, sep = ",")
colnames(y2015) <- c("Name","Gender","#Named2015")
```

B. Displaying the last 10 rows of the data frame y2015
```{r, echo=TRUE}
tail(y2015, 10)
```
These last ten rows are particularly interesting becasue they are names that are all given to males, but also that they have all be uitilzed or recorded exactly 5 times.


C. The great merger: combining y2015 and y2016
```{r, echo=TRUE}
final <- merge(x=y2016,y=y2015,union("Name","Gender"),all = FALSE)
```

### Question 3: Data Summary

A. Creation of the new column "Total" in final adding 'amount of children' in 2015 and 2016.
```{r, echo=TRUE}
final$Total <- final$`#Named2016`+final$`#Named2015`
#Verify the sum equates to the number reported in 2015 and 2016 combined of: 7,239,231.
sum(final$Total)
```

B. Sorting the data by 'total' to discover top 10 names.
```{r, echo=TRUE}
# Shows names with the highest count in decending order
final<-final[order(final$Total, decreasing = TRUE),]
head(final,n=10)
```
Names, in order, are as follows: Emma, Olivia, Noah, Liam, Sophia, Ava, Mason, William, Jacob, and Isabella.

C. Removing the boys and returning the name of girls with the highest counts.
```{r, echo=TRUE}
finalgirls <- subset(final,final$Gender=="F")
head(final, n=10)
```

D. Write the returned names with highest usage/count to a CSV file without the other columns.
``` {r, echo=TRUE}
write.csv(dplyr::select(finalgirls[1:10,],-"Gender",-"#Named2016", -"#Named2015"), row.names=FALSE, file = "MostPopularGirlNames.csv" )
```

### Upload to GitHub
