---
title: "HW3"
author: "Shane W."
date: "January 28, 2019"
output: html_document
---
# Lecture Assignment 3
  
## Questions
  
### Question 1 Cloning
  
New directory to store the repo

$ mkdir Git_Clones

Navigate to newly created directory

$ cd Git_Clones

Clone Repository to this newly created directory

$ git clone git@github.com:awesomedata/awesome-public-datasets.git

### Question 2
a. Read in the titanic.csv
```{r, echo=TRUE}
getwd()
ti <- read.csv(file = "Git_Clones/titanic.csv", header=TRUE , sep=',')
```

b. Female & Male Count
``` {r, echo=TRUE}
f_count <- sum(ti$Sex == "female")
f_count
m_count <- sum(ti$Sex == "male")
m_count
plot(ti$Sex, xlab = "Sex", ylab = "Total Number of Each Sex", main = "Frequency of Females & Males Onboard the Titanic")
```

c. Means of Age, Fare and Surviavl
```{r, echo=TRUE}
means_ti <-data.frame(ti$Age, ti$Fare, ti$Survived)
sapply(means_ti, mean, na.rm =TRUE)
```

### Question 3

```{r, echo=TRUE}
sleepfunction <- function(x){

  ##Read It In 
  sleepfile <- read.csv(file = x, header = TRUE, sep = ",")
  
  #a. Objects for median age, min/max duration of sleep
  # and mean and standard deviation of RSES
  median_age <- median(sleepfile$Age,na.rm = TRUE)
  min_duration <- min(sleepfile$Duration,na.rm = TRUE)
  max_duration <- max(sleepfile$Duration,na.rm = TRUE)
  mean_rses <- mean(sleepfile$RSES,na.rm = TRUE)
  sd_rses <- sd(sleepfile$RSES,na.rm = TRUE)
  
  #b. Create a Data Frame contianing median age, the ?g and ?m of RSES,
  #both divided by 5 and the range of the duration of sleep.
  info <- data.frame(median_age, mean_rses/5, sd_rses/5, max_duration-min_duration)
  
  #c. Set column names of the previously created data frame
  columns <- c("MedianAge", "SelfEsteem", "SE_SD", "DurationRange")
  colnames(info) <- columns
 
  #d. Round values in each column in the data frame to two digits
  info <- round(info, 2)
  
  #e. Print
  info
}
```

#### Print the Function
```{r, echo=TRUE}
sleepfunction("Git_Clones/sleep_data_01.csv")
```

### Question 4

a. The Package
``` {r, echo=TRUE}
install.packages("fivethirtyeight", repos = "http://cran.us.r-project.org")
```

b. List Datasets in FiveThirtyEight and Assign22nd toa dat frame
```{r, echo=TRUE}
library(fivethirtyeight)
df <- college_recent_grads
```
c. Providing additional detailed list of the datasets
```{r, echo=TRUE}
vignette("fivethirtyeight", package = "fivethirtyeight")
```

d. Dimensions and column names of the data frame.
```{r, echo=TRUE}
dim(df)
colnames(df)
```

### Question 5
a. Column Names and count
```{r, echo=TRUE}
colnames(df)
#column Count
ncol(df)
```

b. Major Count/Major Category
```{r, echo=TRUE}
library(plyr)
major_count <- count(df, "major_category")
```

c. Output Graph of Frequency of Majors from Major_Count
```{r, echo=TRUE}
par(las=2)
barplot(major_count$freq, main = "Freq. of Majors from Recent Grads", horiz = TRUE, xlab = "Frequency", ylab = "College Major", col = c("cyan","cyan1","cyan2","cyan3","cyan4","deeppink","deeppink2","deeppink3","deeppink4","darkorchid","darkorchid1","darkorchid2","darkorchid3","darkorchid4", "aquamarine"), names.arg= major_count$major_category)
```

d. Write df to CSV
```{r, echo=TRUE}
write.csv(df, file = "Major_Gradudates.csv", row.names=FALSE)
```


### Question 6
Link to Homework Repository
+
Link to this homework
+