---
title: "Homework4.6"
author: "Shane W."
date: "February 5, 2019"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "Homework 4"
author: "Shane W."
date: "February 5, 2019"
output: html_document
---

# Harry Potter
```{r echo=TRUE}
#Housekeeping
getwd()
library(tidyr)
library(rvest)
library(dplyr)
```

a. Review the data at link: http://www.imdb.com/title/tt1201607/fullcredits?ref_=tt_ql_1
b. Scrape it all.
``` {r echo=TRUE}
persons <- read_html("http://www.imdb.com/title/tt1201607/fullcredits?ref_=tt_ql_1")
personslist <- persons %>% html_nodes(xpath = '//*[@id="fullcredits_content"]/table[3]') %>% html_table(header=TRUE)
personsdf <- personslist[[1]]
```

c. Clean it all.
* Naming and Removing Empty Observations
``` {r echo= TRUE}
#Name 'em and remove empties
colnames(personsdf) <- c("1","Actor","2","Character")
personsdf = select(personsdf, "Actor", "Character")
```

* Dealing with duplicative Mr. Warwick and Extra Row (92)
``` {r echo=TRUE}
getwd()
#Duplicate Management
personsdf$Character[10] <- 'Griphook / Professor Filius Flitwick'
#Remove the 92
personsdf <- personsdf[-c(92)]
```

d. FirstName and Surname
``` {r echo=TRUE}
personsdf <- personsdf %>% separate(Actor, c("FirstName","Surname"), "(?=[^ ]+$)", extra = "merge")
```

e. Presentation Confirmation
``` {r echo=TRUE}
head(personsdf, 10)
```

# 2 SportsBall
a. Review ESPN Website to discover 'Shooting Statistics' http://www.espn.com/nba/team/stats/_/name/sa/san-antonio-spurs). 

b. Scrape
```{r echo=TRUE}
shots <- read_html("http://www.espn.com/nba/team/stats/_/name/sa/san-antonio-spurs)")
shotslist <- shots %>% html_nodes(xpath='//*[@id="fittPageContainer"]/div[2]/div[5]/div[1]/div/article/div/section/section/section[2]/table') %>% html_table(fill=TRUE)
shotsdf <- shotslist[[1]]
```

c. More House Keeping (clean)
```{r echo=TRUE}
shotsdf <- shotsdf[-c(1), ]
shotsdf <- shotsdf[-c(18), ]
shotsdf <- shotsdf[ , -c(15:258) ]
shotsdf <- shotsdf[-c(17), ]
shotsdf <- shotsdf[-c(33), ]

#Vector to store names then input into Columns
name_vector <- as.vector(shotsdf$X1[2:16])
shotsdf <- shotsdf[-c(1:16), ]

vector_col <- as.character(shotsdf[1,])
vector_col <- append(vector_col, "Name", after = 0)
shotsdf <- shotsdf[-c(1), ]

shotsdf <- cbind(name_vector, shotsdf)
colnames(shotsdf) <- vector_col

#Team Position Separation
shotsdf <- shotsdf %>% separate(Name, c("Name", "Position"), "(?=[^ ]+$)", extra = "merge")

#Numeric Formatting
shotsdf[3:16] <- sapply(shotsdf[3:16], as.numeric)
sapply(shotsdf, class)
#First 10
head(shotsdf, 10)
```

d. Bar Chart
``` {r echo=TRUE}
colors <- RColorBrewer::brewer.pal(length(unique(shotsdf$Position)), name = "Set2")
shotsdf$color <- colors[as.factor(shotsdf$Position)]
par(las=2)
barplot(shotsdf$`FG%`, main = "San Antonio Spurs Field Goal % Per Game", horiz = TRUE, xlab = "Field Goal %", col = shotsdf$color, names.arg = shotsdf$Name, cex.names = 0.7)
```